Illuminating a Dark Lens : A Type Ia Supernova Magnified by Galaxy Cluster Abell 2744

### 2015-01-22 snTomas.tex
updated spectroscopy, phot classification sections

\shorttitle{A \SNIa Behind Abell 2744}
\shortauthors{Rodney et al.}

@@

\begin{abstract}
SN \tomas\ is a Type Ia Supernova (\SNIa) discovered at $z=1.33$
behind the galaxy cluster Abell 2744 ($z=0.308$). This SN has a
projected separation from the cluster core of $\sim$40\arcsec, closer
than any other cluster-lensed \SNIa.  As such, it provides the first
opportunity to confront gravitational lens models of galaxy clusters
with the direct measurement of an absolute magnification at the edge
of the strong-lensing region.  We derive a tightly constrained measure
of the peak apparent magnitude, corrected for light curve shape and
exinction.  In a cosmology-independent analysis, we find that \tomas\
is $0.71\pm0.12$ magnitudes brighter than unlensed \SNeIa\ at similar
redshift, implying a lensing magnification of $\mu_{\rm
obs}=1.9\pm0.2$.  Predicted magnifications from 7 independent groups
are systematically biased to higher values, with a mean of $\mu_{\rm
mod}=2.4\pm0.3$ and some models disagreeing by $>6\sigma$.  The most
significant discrepancies arise from models with a strict ``light
traces mass'' assumption.  We evaluate possible causes for this bias,
including variation of the mass-to-light ratio in the nearest cluster
member galaxy.  A sample of \textcolor{red}{$\sim$10??} \SNeIa\ behind
any single cluster could provide a robust evaluation of systematic
biases in lens models.  Until such a sample exists, it is advisable to
increase the estimated uncertainty of any predicted magnification
by an amount comparable to the dispersion from all available lens
models.

@@

Massive galaxy clusters can be used as cosmic telescopes to magnify
distant background objects through gravitational lensing.  This can
substantially increase the reach of deep imaging surveys, and has
recently been used to discover candidate proto-galaxies formed in the
first Gyr after the Big
Bang \citep{Zheng:2012,Coe:2013,} 
\textcolor{red}{(cite other high-z galaxy candidates discovered with lensing)}

@@

In Section~\ref{sec:DiscoveryAndFollowup} we present the discovery and
follow-up observations of SN \tomas at $z=1.31$, discovered behind the
galaxy cluster Abell 2744.  Sections~\ref{sec:Spectrum} and \ref{sec:LightCurve}
describe the spectroscopy and photometry of this SN, leading to a
classification of the object as a normal Type Ia SN.  In
Section~\ref{sec:LensingMagnification} we make a direct measurement of
the magnification of this source due to gravitational lensing, and
compare to predicitions from lens models.  Finally,
Section~\ref{sec:Discussion} discusses the tension between our
magnification measurement and the lens models, with implications for
the systematic error budget in magnification estimates for other
high-$z$ lensed sources.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{FIG/discovery_image}
\caption{  \label{fig:DiscoveryImage}
SN \tomas\ in the Abell 2744 field.  The left panel shows a
UV/Optical/IR color composite image constructed from all available HST
imaging of the Abell 2744 cluster field.\footnote{Image Credit: NASA,
ESA, and J. Lotz, M. Mountain, A. Koekemoer, and the HFF Team
(STScI)}  The inset panels at right show F814W imaging of the
immediate vicinity of SN \tomas, approximately 40\arcsec\ from the
center of the cluster.  The top panel shows the template image,
combining all data prior to the SN appearance.  Labeled ellipses mark the nearest galaxies and their redshift constraints: a photometric redshift for the most likely host galaxy is marked in blue, and the spectroscopic redshift for a likely background galaxy is given in yellow. The bottom panel is
constructed from all HFF F814W imaging taken while the SN was detectable, and marks the SN location with an arrow.}
\end{center}
\end{figure*}

@@

\section{Spectrum}
\label{sec:Spectrum}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{FIG/specfit}
\caption{  \label{fig:SpecFit}
Best-fit Type Ia spectral template matches to the SN \tomas\ spectrum.
When the templates are not warped, an acceptable fit can be found with
a normal Type Ia at $z\sim1$ (top), or at $z=1.31$ (middle).  Introducing a smooth 3rd-order polynomial to warp the shape of the template pseudo-continuum makes the $z=1.31$ solution far superior.}
\end{center}
\end{figure}

A spectrum of SN \tomas\ was collected with the ACS G800L grism on
2014 June 4 and 7, using 5 HST orbits from the FrontierSN program for
a total spectroscopic exposure time of $\sim$10 ksec.  Details of the
observations are given at the bottom of
Table~\ref{tab:Photometry}. The grism data were processed and the
target spectrum was extracted using the custom pipeline employed by
the Grism Lens Amplified Survey from Space program (GLASS; PI:Treu,
PID:13459). \textcolor{red}{Is there a citation for this? or more to
say here?}  Figure~\ref{fig:spectrum} shows the composite 1-D ACS
grism spectrum, combining all available G800L exposures.  The spectrum
is largely free of contamination, because as the SN is well separated
from nearby foreground sources and is hosted by a diffuse and
optically faint galaxy.  Thus, the SN spectral features can be
unambiguously identified, most notably the red slope of the continuum
and a prominent absorption feature at $\sim$8700\AA.  However, the
signal to noise ratio (S/N) for the host galaxy spectrum was too weak
to yield any additional constraints on the host type or redshift.

@@

\subsection{SNID Fitting}
\label{sec:SNID}

@@

Using SNID to fit the \tomas\ spectrum, we find strong evidence that
the spectral type is a normal Type Ia, with $>$97\% of the matching
SEDs coming from Type Ia spectra.  
In SNID the goodness of fit is evaluated primarily through the {\it rlap} parameter, which measures the degree of wavelength overlap and the strength of the cross-correlation peak.  For SN \tomas\ the best matching Type Ia template is the normal Type Ia SN 2004fu at z=1.321 and age=2.4 days past peak, which delivers {\it rlap}=20.8.
Despite the relatively small rest-frame wavelength window of this spectrum, the SNID classification is quite definitive: \textcolor{red}{no \CCSN\ template achieves an {\it rlap} value better than 5.0 at any redshift.}

The best-fit Type Ia SEDs are also
consistent in redshift at $z=1.32\pm0.01$, and in phase at $0.4\pm1.7$
rest-frame days from peak (meaning MJD$_{\rm pk}$=56813$\pm$4).  At
this redshift, the absorption at $\sim$8700\AA\ corresponds to the
blended \ion{Ca}{2} H\&K features.  This \ion{Ca}{2} absorption is
commonly seen in Type Ia SN spectra near maximum light, although it is
also prominent in the spectra of Type Ib and Ic core collapse SNe
(\CCSNe).  The red color of the \tomas\ SED is qualitatively
consistent with a redshift of $z>1$ -- although this information was
not used by SNID for the template matching.  As we will see in
Section~\ref{sec:LightCurve}, this spectral classification of
SN \tomas\ is supported by the photometric information, which is also
most consistent with a Type Ia SN at $z=1.3$.

\subsection{Extended Type Ia Template Matching}
\label{sec:FittingWithAdditionalTypeIaTemplates}

To refine the redshift and phase constraints on \tomas, we next fit
the spectrum with a custom spectral matching program that employs a
library of Type Ia SN SEDs.  This library is similar to the Type Ia
spectral set used by SNID, but also includes more recent SNe with
well-observed spectral time series that extend to rest-frame UV
wavelengths (e.g. SN 2011fe and 2014J).  We first use an approach
similar to the SNID algorithm: warping the pseudo-continuum of each
template spectrum by dividing out a 3$^{\rm rd}$-order polynomial to match the
observed SED of SN \tomas.  From this analysis we find results that
are consistent with the SNID fits: a redshift of $z=1.31\pm0.01$ and a
phase of $0\pm3$ rest-frame days.

Finally, we repeat the fitting, but without any warping of the
templates to account for differences in the continuum shape.  In this
iteration we only allow each template SED to be scaled in flux
coherently at all wavelengths.  Here we again find that the \tomas\
SED is well matched by a normal Type Ia SN (SN 2011fe) at redshift
$z=1.31\pm0.01$.  Without the continuum warping, an alternative fit
also arises: the normal Type Ia SN 2011iv at
$z=0.98\pm0.01$. Formally, this match provides a better fit to the
unwarped \tomas\ spectrum, although this redshift is at odds with the
host galaxy photo-z ($1.5\pm0.2$), and we will see in the following
section that the photometric data is incompatible with a normal Type
Ia SN at $z\sim1.0$.

\section{Light Curve}
\label{sec:LightCurve}

@@

\subsection{Photometric Classification}
\label{sec:PhotometricClassification}

As a check on the spectral classification of SN \tomas\
(Section~\ref{sec:SNID}), we independently classified the SN using a
Bayesian photometric classifier.  This classification code uses the
{\tt sncosmo} software
package\footnote{\url{http://sncosmo.github.io/}} to simulate SN light
curves at a range of redshifts and evaluate the classification
probability using traditional Bayesian model selection \citep[as
in][]{Jones:2013,Rodney:2014,Graur:2014,Rodney:2015}.  In this
analysis we represent normal Type Ia SNe with the SALT2
model \citep{Guy:2010}, and \CCSNe\ with 42 discrete templates (26
Type II and 16 Type Ib/c) drawn from the template library of the
SuperNova Analysis software \citep[SNANA,][]{Kessler:2009a}.  Due to
the expected impact of gravitational lensing magnification, we do not
include any prior on the intrinsic luminosity for any SN sub-class.

From this photometric analysis we derive a Type Ia classification
probability of $p(\rm Ia|{\bf \rm D})=XX\%$.  Marginalizing over the
light curve shape and color parameters of the SALT2 model, we extract
a posterior probability distribution in redshift that is well
described by a single Gaussian centered at $z=1.32\pm0.03$.

\textcolor{red}{Light curve fitting with MLCS2k2}

determine a photometric classification

derive a constraint on the time of peak

\begin{figure*}
\begin{center}
\includegraphics[width=0.49\textwidth]{FIG/lcfit_mlcs2k2_ABmag}
\includegraphics[width=0.49\textwidth]{FIG/specfit_11fe_t-3_z131}
\caption{ {\it (Left)} Light curve fit using MLCS2k2. 
{\it (Right)} Spectral template match to the HST ACS G800L SN
spectrum.  Assuming minimal reddening, the best-fit template is from
SN 2011fe at $z=1.31$ and $t=-3$ rest-frame days before peak
brightness.  Allowing a correction for the broad SED shape using
3rd-order polynomials, the best match is from SN 2012cg at $z=1.31$
and $t=+3 days$.
\label{fig:mlcsfit} }
\end{center}
\end{figure*}

@@

Proposal for a survey to build a bigger sample : HST GO, Snapshot, ground-based.

>>>>

\shorttitle{A Type Ia SN Behind Abell 2744}
\shortauthors{Rodney et al.}

@@

\begin{abstract}
SN \tomas\ is a Type Ia Supernova (\SNIa) discovered at $z=1.33$
behind the galaxy cluster Abell 2744 ($z=0.308$). This SN has a
projected separation from the cluster core of $\sim$40\arcsec, closer
than any other cluster-lensed \SNIa.  As such, it provides the first
opportunity to confront gravitational lens models of galaxy clusters
with the direct measurement of an absolute magnification at the edge
of the strong-lensing region.  We derive a tightly constrained measure
of the peak apparent magnitude, corrected for light curve shape and
exinction.  In a cosmology-independent analysis, we find that \tomas\
is $0.71\pm0.12$ magnitudes brighter than unlensed \SNeIa\ at similar
redshift, implying a lensing magnification of $\mu_{\rm
obs}=1.9\pm0.2$.  Predicted magnifications from 7 independent groups
are systematically biased to higher values, with a mean of $\mu_{\rm
mod}=2.4\pm0.3$ and some models disagreeing by $>6\sigma$.  
\textcolor{red}{TODO: summarize lensing discussion.}
%The most
%significant discrepancies arise from models with a strict ``light
%traces mass'' assumption.  We evaluate possible causes for this bias,
%including variation of the mass-to-light ratio in the nearest cluster
%member galaxy.  A sample of \textcolor{red}{$\sim$10??} \SNeIa\ behind
%any single cluster could provide a robust evaluation of systematic
%biases in lens models.  Until such a sample exists, it is advisable to
%increase the estimated uncertainty of any predicted magnification
%by an amount comparable to the dispersion from all available lens
%models.

@@

Massive galaxy clusters can be used as cosmic telescopes to magnify
distant background objects through gravitational lensing.  This can
substantially increase the reach of deep imaging surveys, and has
recently been used to discover candidate proto-galaxies formed in the
first Gyr after the Big
Bang \citep{Zheng:2012,Coe:2013} 
\textcolor{red}{(cite other high-z galaxy candidates discovered with lensing)}

@@

In Section~\ref{sec:DiscoveryAndFollowup} we present the discovery and
follow-up observations of SN \tomas at $z=1.31$, discovered behind the
galaxy cluster Abell 2744.  Sections~\ref{sec:Spectroscopy} and \ref{sec:PhotometricClassification}
describe the spectroscopy and photometry of this SN, leading to a
classification of the object as a normal Type Ia SN.  In
Section~\ref{sec:LensingMagnification} we make a direct measurement of
the magnification of this source due to gravitational lensing, and
compare to predicitions from lens models.  Finally,
Section~\ref{sec:Discussion} discusses the tension between our
magnification measurement and the lens models, with implications for
the systematic error budget in magnification estimates for other
high-$z$ lensed sources.

@@

\begin{figure*}
\begin{center}
%\includegraphics[width=\textwidth]{FIG/discovery_image}
\includegraphics[width=\textwidth]{FIG/discovery_image_lowres}
\caption{  \label{fig:DiscoveryImage} 
SN \tomas\ in the Abell 2744 field.  The left panel shows a
UV/Optical/IR color composite image constructed from all available HST
imaging of the Abell 2744 cluster field.  The inset panels at right
show F814W imaging of the immediate vicinity of SN \tomas,
approximately 40\arcsec\ from the center of the cluster. The top panel
shows the template image, combining all data prior to the SN
appearance.  Labeled ellipses mark the nearest galaxies and their
redshift constraints: a photometric redshift for the most likely host
galaxy is marked in blue, and the spectroscopic redshift for a likely
background galaxy is given in yellow. The bottom panel is constructed
from all HFF F814W imaging taken while the SN was detectable, and
marks the SN location with an arrow.  (Left panel image credit: NASA,
ESA, and J. Lotz, M. Mountain, A. Koekemoer, and the HFF Team (STScI))
}
\end{center}
\end{figure*}

@@

\section{Spectroscopy}
\label{sec:Spectroscopy}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{FIG/specfit}
\caption{  \label{fig:SpecFit}
Redshift and age determination from spectral template matching to the
the SN \tomas\ maximum light spectrum.  The y axis plots flux in
arbitrary units, and the x axis marks wavelength in \AA\ with the
observer-frame on the bottom and rest-frame on the top.
The \tomas\ spectrum observed with the
HST ACS G800L grism is shown in black, overlaid with model fits
derived from a library of Type Ia templates that have extended
rest-frame UV coverage.  {\it Top}: The best match is at $z=1.31$ with
age=$+3$ days, from the normal Type Ia SN 2012cg template when using a
smooth 3rd-order polynomial to warp the shape of the template
pseudo-continuum.  When the templates are not warped, an acceptable
fit can be found with a normal Type Ia at $z=1.31$ (middle) or at
$z\sim1$ (bottom), although the latter is inconsistent with the host
galaxy redshift prior and the light curve. No \CCSN\ templates can
provide a statistically acceptable fit at any redshift, within the age
constraints imposed by the light curve.}
\end{center}
\end{figure}

A spectrum of SN \tomas\ was collected with the ACS G800L grism on
2014 June 4 and 7, when the SN was very near to its peak brightness.
The observations -- listed at the bottom of Table~\ref{tab:Photometry}
-- used 5 HST orbits from the FrontierSN program for a total
spectroscopic exposure time of $\sim$10 ksec.  The grism data were
processed and the target spectrum was extracted using the custom
pipeline employed by the Grism Lens Amplified Survey from Space
program (GLASS; PI:Treu, PID:13459). \textcolor{red}{Is there a
citation for this? or more to say here?}

Figure~\ref{fig:SpecFit} shows the composite 1-D ACS grism spectrum,
combining all available G800L exposures, overlaid with SN model fits
that will be described below.  The spectrum is largely free of
contamination, because the orientation was chosen to avoid nearby
bright sources and the host galaxy is diffuse and optically faint.
Thus, the SN spectral features can be unambiguously identified, most
notably the red slope of the continuum and a prominent absorption
feature at $\sim$8700\AA.  However, the signal to noise ratio (S/N)
for the host galaxy spectrum was too weak to yield any additional
constraints on the host type or redshift.

@@

\subsection{Classification with SNID}
\label{sec:SNID}

@@

In SNID the goodness of fit is evaluated primarily through the {\it
rlap} parameter, which measures the degree of wavelength overlap and
the strength of the cross-correlation peak.  Typically, an {\it rlap}
value $>5$ is required to be considered an acceptable match.

To match the SN \tomas\ spectrum we use conservative constraints on
age and redshift: limiting the age to $\pm$5 rest-frame days of peak
brightness and $0.8<z<1.8$, consistent with the SN light curve and
host galaxy photo-$z$.  With these constraints we find that the only
acceptable match is a normal Type Ia SN near $z=1.3$. The best match
has {\it rlap}$=8.7$, using the normal Type Ia SN 2005cf at $z=1.35$
and age=-2.2 rest-frame days before peak.  Within these constraints,
the best non-Ia matches all have {\it rlap}$<2.5$.

The {\tt SNID} library can generate an acceptable \CCSN\ match only
when we remove all age and redshift constraints, In this case the best
non-Ia match is the Type Ic SN 1997ef, which delivers {\it rlap}$=6.8$
at $z=0.51$ and age=47.3 rest-frame days past peak.  This is not as
good a fit as the best Type Ia models, is at odds with the host galaxy
redshift prior, and is strongly disfavored by the shape and colors of
the SN light curve (see Section~\ref{sec:PhotometricClassification}).

From the preceding analysis, we conclude that \tomas\ is a Type Ia SN
at $z\approx1.3$.  At this redshift, the absorption at $\sim$8700\AA\
corresponds to the blended \ion{Ca}{2} H\&K features.
This \ion{Ca}{2} absorption is commonly seen in Type Ia SN spectra
near maximum light, although it is also prominent in the spectra of
Type Ib and Ic core collapse SNe (\CCSNe).  The red color of
the \tomas\ SED is qualitatively consistent with a redshift of $z>1$
-- although this information was not used by {\tt SNID} for the
template matching.  As we will see in Section~\ref{sec:PhotometricClassification},
this spectral classification of SN \tomas\ is reinforced by the
photometric information, which also supports classification as a Type
Ia SN at $z=1.3$.

\subsection{Spectroscopic Redshift}
\label{sec:SpecRedshift}

To refine the redshift and phase constraints on \tomas, we next fit
the spectrum with a custom spectral matching program that employs a
library of Type Ia SN SEDs.  This library is similar to the Type Ia
spectral set used by SNID, but also includes more recent SNe with
well-observed spectral time series that extend to rest-frame UV
wavelengths (e.g. SN 2011fe and 2014J).  We first use an approach
similar to the SNID algorithm: warping the pseudo-continuum of each
template spectrum by dividing out a 3$^{\rm rd}$-order polynomial to
match the observed SED of SN \tomas.  From this analysis we find
results that are consistent with the SNID fits: a redshift of
$z=1.31\pm0.01$ and a phase of $0\pm3$ rest-frame days. The
best-fitting spectral template is the normal Type Ia SN 2012cg, shown
in the bottom panel of Figure~\ref{fig:SpecFit}, which has $\chi^2$
per degree of freedom $\nu$ equal to 42.1/87.

Finally, we repeat the fitting, but without any warping of the
templates to account for differences in the continuum shape.  In this
iteration we only allow each template SED to be scaled in flux
coherently at all wavelengths.  As shown in Figure~\ref{fig:SpecFit},
we again find that the \tomas\ SED can be matched by a normal Type Ia
SN (SN 2011fe) at redshift $z=1.31\pm0.01$.  Without the continuum
warping, an alternative fit also arises: the normal Type Ia SN 2011iv
at $z=0.98\pm0.01$. Formally, this match provides a slightly better
fit to the unwarped \tomas\ spectrum, although the fit is notably poor
at $\sim8700$\AA\ where the most significant absorption feature is
found. Furthermore, a redshift $z\sim1$ is at odds with the host
galaxy photo-z ($1.5\pm0.2$), and we will see in the following section
that the photometric data is incompatible with a normal Type Ia SN at
$z\sim1.0$.

Setting aside the $z\sim1$ solution, all other template matches
provide a consistent redshift constraint of $z=1.31\pm0.01$,
regardless of whether the templates are warped to match the SN \tomas\
continuum shape.  The inferred age from these fits is $0\pm3$
rest-frame days from peak brightness, which is also consistent with
the observed light curve.

\section{Photometric Classification}
\label{sec:PhotometricClassification}

@@

As a check on the spectral classification of SN \tomas\
(Section~\ref{sec:SNID}), we independently classified the SN using a
Bayesian photometric classifier.  This classification code uses the
{\tt sncosmo} software
package\footnote{\url{http://sncosmo.github.io/}} to simulate SN light
curves at a range of redshifts and evaluate the classification
probability using traditional Bayesian model selection \citep[as
in][]{Jones:2013,Rodney:2014,Graur:2014,Rodney:2015}.  In this
analysis we represent normal Type Ia SNe with the SALT2
model \citep{Guy:2010}, and \CCSNe\ with 42 discrete templates (26
Type II and 16 Type Ib/c) drawn from the template library of the
SuperNova Analysis software package \citep[SNANA,][]{Kessler:2009a}.
Likelihoods are defined by comparing the observed fluxes to model
predictions in all passbands where the model is defined.  In practice,
this means we exclude the F435W and F606W bands, which are too blue
for our models at $z>1$.

The \CCSN\ models have free parameters for date of peak brightness
($t_{\rm pk}$), amplitude, and redshift ($z$). Due to the expected
impact of gravitational lensing magnification, we do not include any
prior on the intrinsic luminosity for any SN sub-class.  We also do
not assign a prior for the SN redshift. This allows our photometric
analysis to provide an independent check on the host galaxy photo-$z$
and spectroscopic redshift (Sections~\ref{sec:HostGalaxy}
and \ref{sec:SpecFit}).

For Type Ia SNe, the SALT2 model has two additional parameters that
control the shape ($x_1$) and color ($c$) of the light curve.  We use
conservative priors here, defined to encompass a range of Type Ia SN
shapes and colors that is broader than typically allowed in
cosmological analyses \citep[see
e.g.][]{Kessler:2009b,Sullivan:2011,Rest:2014}. For $x_1$ the prior is
a bifurcated Gaussian distribution with mean $\bar{x}_1=0$, dispersion
$\sigma_{x_1}^+={0.9}$ and $\sigma_{x_1}^-={-1.5}$.  The prior for the
color parameter $c$ has $\bar{c}=0.0$, $\sigma_c^-=0.08$, and
$\sigma_c^+=0.54$.  The $c$ parameter in SALT2 combines intrinsic SN
color and extinction due to dust, so the large red tail of this
distribution allows for the possibility of several magnitudes
of dust extinction along the \tomas\ line of sight.

We also assign a class prior for each of the three primary SN
sub-classes (Type Ia, Ib/c, and II), using a fixed relative fraction for
each sub-class as determined at $z=0$ by \citet{Smartt:2009}
and \citet{Li:2011a}.  A more rigorous classification would extrapolate
these local SN class fractions to higher redshift using models or
measurements of the volumetric SN rate.  For simplicity, we do not
vary the class priors with redshift, and in practice these priors do
not have any significant impact on the resulting classification.

The final photometric classification probability for SN \tomas\ is
$p({\rm Ia}|{\bf \rm D})=1.0$, with the classification
probability from all \CCSN\ sub-classes totaling less than $10^{-100}$.  The
marginal posterior distribution in redshift for the Type Ia model is
sharply peaked at $z=1.36\pm0.02$, which is $<2.5\sigma$ from
the spectroscopic redshift of $z=1.31\pm0.01$ derived in
Section~\ref{sec:SpecRedshift}.  The time of peak brightness is also
tightly constrained at $t_{\rm pk}=56816.0\pm0.2$, which means the
spectroscopic observations were collected within 2 rest-frame days of
the epoch of peak brightness, consistent with our spectroscopic
analysis.

\section{Light Curve Fitting}
\label{sec:LightCurveFitting}

With the spectroscopic type and redshift securely defined as a normal
Type Ia SN at $z=1.3$, we now turn to fitting the light curve with
Type Ia templates to measure the distance modulus.  Here we use two
independent light curve fitters: first the SALT2 model described
above, and then the MLCS2k2 model from \citep{Jha:2007}.

\subsection{SALT2 Fit}
\label{sec:SALT2Fit}

in \citep{Patel:2014}:   $\alpha=1.367\pm0.086$,
$\beta=3.179\pm0.101$, $M=-19.12\pm0.03$.

For the SALT2 Type Ia model one can define a shape- and color-corrected apparent
B-band magnitude using 
$m_{\rm B}^\prime = m_{\rm B} + \alpha x_1 - \beta c$.

For the SALT2 model we fix the model parameters to the values
derived in the \citet{Rest:2014} analysis of the Pan-STARRS1 SN sample:
$\alpha=0.147$, $\beta=3.13$, $M_B=-19.34$.

Comparing salt2 color to Av \citep{Kessler:2009b}:
$c = (0.464 ± 0.021)AV − (0.121 ± 0.014)$

from \citet{Patel:2014}:
``Finally, to ensure a consistent zeropoint between the SALT2 and
MLCS2k2 distance moduli, we applied both methods to a sample of SDSS
Supernova Survey SNe Ia from Holtzman et al. (2008) and Kessler et
al. (2009a). We added a zeropoint correction of 0.20 mag to the
distance moduli reported by SNANA in the MLCS2k2 fit (dmMLCS2k2), to
put them on the same scale as the SALT2 distances (dmSALT2).''

\subsection{MLCS2k2 Fit}
\label{sec:MLCS2k2Fit}

As in \citep{Patel:2014}.

$R_v$ fixed to 1.9.

for Rv = 1.9, the calibrated distance is: $\mu = \mu_{\rm mlcs}-0.2006$.

\begin{figure}
\begin{center}
\includegraphics[width=0.49\textwidth]{FIG/lcfit_mlcs2k2_ABmag}
\caption{  Light curve fit using MLCS2k2. 
\label{fig:mlcsfit} }
\end{center}
\end{figure}

@@

Design elements for a survey to build a bigger sample : HST GO, Snapshot, ground-based.
